\cvsection{Experience}
\begin{cventries}
  \cventry
    {Keio University}
    {Yokohama, JAPAN}
    {Post-doctoral fellow on Autonomous Driving}
    {Nov. 2017 - present}
    {
      \begin{cvitems}
        \item {\textbf{Study how machine-learning can benefit to Autonomous Driving.}}
        \item {Develop an Android application to collect, transform and send vehicles information to a Management System.}
        \item {Implement a simulation platform to study different services.}
      \end{cvitems}
    }
  \cventry
    {Institut Mines-T\'{e}l\'{e}com}
    {Paris, FRANCE}
    {Editor for IMT Massive Open Online Course (MOOC) on Digital Fabrication }
    {Feb. 2017 - Aug. 2017}
    {
      \begin{cvitems}
        \item {\textbf{Review and enhance contents of existing MOOCs.}}
        \item {Set up ``hands-on'' lab works to complete online courses.}
        \item {Develop a MOOC focusing on understanding energy principles via Digital Fabrication.}
      \end{cvitems}
    }
  \cventry
    { }
    { }
    {\hspace*{0,7cm} ICT Architect for the European Project ``Smart Energy Aware Systems (SEAS)''}
    {Mar. 2015 - Jan. 2017}
    {
      \begin{cvitems}
      	\item {\textbf{Study the best way to integrate domestic energy productions within main energy networks/markets.}}
        \item {Design an innovative ICT Architecture compliant with IoT technology, other standards and existing platforms.}
        \item {Implement a Proof-of-Concept to demonstrate its benefits and evaluate it with real scenarios.}
%        \begin{cvspecificitems}
%      		\item Rewarded 
%      	\end{cvspecificitems}
      \end{cvitems}
    }
  \cventry
    {CISCO \& T\'{e}l\'{e}com Bretagne}
    {Rennes, FRANCE}
    {Research \& Development Engineer}
    {Mar. 2010 - Aug. 2010}
    {
      \begin{cvitems}
        \item {\textbf{Adapt Universal Plug and Play (UPnP) standard to IPv6.}}
        \item {Enhance an existing UPnP stack with IPv6 capabilities.}
        \item {Implement a security patent to prevent corrupted devices from interfering.}
      \end{cvitems}
    }
%  \cventry
%    {Orange Labs}
%    {Cesson-S\'{e}vign\'{e}, FRANCE}
%    {Mobility demonstrator performance evaluation and optimization}
%    {Mar. 2009 - Aug. 2009}
%    {
%      \begin{cvitems}
%        \item {\textbf{Integrate new devices to the demonstrator.}}
%        \item {Evaluate its performance and solve issues.}
%        \item {Optimize time spent during handover.}
%      \end{cvitems} 
%    }
  \cventry
    {HTC Europe Co. Ltd}
    {Slough, UNITED-KINGDOM}
    {Commercialization Product Manager \& Technical Manager}
    {Aug. 2007 - Jun. 2008}
    {
      \begin{cvitems}
        \item {\textbf{Manage Smartphones roadmap and projects delivery for UK and East-Europe.}}
        \item {Set up and manage a full project for East-Europe market.}
        \item {Manage technical projects -- Resolving issues and satisfying customers requirements.}
      \end{cvitems}
    }
%  \cventry
%    {NiCT}
%    {Tokyo, JAPAN}
%    {Study of Microstrip patch antennas}
%    {Jun. 2006 - Aug. 2006}
%    {\quad \quad Build and experiment patch antennas.}
  
\end{cventries}
