\cvsection{Research and Teaching Activities}
\cvsubsection{Ph.D. thesis}
\begin{cvhonors}
  \cvhonortwo
    {Title}
    {Service-based Networking applied to Machine-to-Machine Communications}
  \cvhonor
    {Prof. Jean-Marie BONNIN}
    {Dr. Laurent TOUTAIN and Dr. Philippe BERTIN}
    {}
    {Director}
  \cventryshort
    {Summary}
    {\begin{justify}
    \quad The network ecosystem offers a diversity of Access Networks (ANs) for devices to connect to. Currently, devices select the AN based on its physical characteristics. However, the best AN satisfying this selection may not be the most suitable one for all services. In addition, the arrival of new constrained devices with the Internet of Things requires that the connection process should be specified for them to benefit from this AN diversity. We proposed a generic, lightweight and service-based announcement mechanism, allowing any device to efficiently select, and so, connect to the best AN for each service. Our mechanism helps Service Providers announce their services on existing networks and helps devices filter ANs based on service availability. Both the impact and effectiveness of this mechanism has been studied on a Machine-to-Machine scenario using simulations and mathematical models.
    \end{justify}}

%\end{cvhonors}

\cvsubsection{Research}
%\begin{cvhonors}
  \cventryshort   
    {Interest}
    {\begin{cvitems}
        \item {Internet of Things -- Architecture, Protocols, Applications and Implementations.}
        \item {Smart Grid -- Energy management, production and consumption coordination as well as interconnection of ``energy actors''.}
        \item {Intelligent Transport System -- Vehicle-to-Vehicle and Vehicle-to-Infrastructure (Grid, Road, etc.) communications as well as different services (Efficient charging, traffic management, etc.).}
        \item {Wireless Mobility and Multihoming -- Handover management, Network selection.}
      \end{cvitems}
      }
  \cventryshort
    {Achievements}
    {\begin{cvitems}
        \item {Set up a complete ``nanogrid'' at T\'{e}l\'{e}com Bretagne -- Photovoltaic panels and batteries interacting with a custom management system and an Electric Vehicle. It includes tools and algorithms to automate and visualize both electricity consumption and production, as well as, manage and optimize them.}
        \item {Contributed to the enhancement of Wi2Me – an android research application collecting Wi-Fi statistics.}
      \end{cvitems}
      }

\cvsubsection{Teaching}
  \cventryshort
    {Experience}
    {\begin{cvitems}
        \item {Participated in the development of a Python teaching application which supports network courses.}
        \item {Prepared and supervised practical lab works and graduate courses for a total of 250 hours of service.}
        \item {Supervised final year students projects and interns.}
        \item {Organized a research seminar with Keio University.}
        \item {Prepared, organized and gave UPnP lectures for professional training.}
      \end{cvitems}
      }
\end{cvhonors}
